\documentclass[a4paper, 12pt]{article}
\usepackage[
    type={CC},
    modifier={by},
    version={4.0},
]{doclicense}                
\setlength{\parindent}{6mm}
\usepackage{amsmath,amsthm,amssymb,amsfonts, mathtools}
\usepackage{graphicx}
\usepackage[margin=1.5in]{geometry}    % For margin alignment
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{pdfpages}
\usepackage[ruled, lined, linesnumbered, commentsnumbered, longend]{algorithm2e}
\usepackage{arevmath}     % For math symbols
\usepackage{exercises}
\usepackage[ruled, lined, linesnumbered, commentsnumbered, longend]{algorithm2e}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\SetKwInput{KwInput}{Input}                % Set the Input
\SetKwInput{KwOutput}{Output}              % set the Output
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{source.bib}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{Alberto Defendi}
\fancyhead[RE,LO]{IoT: week 6 solutions}
\fancyfoot[LE,RO]{\thepage}

\title{Problem solutions 6}
\author{Alberto Defendi - alberto.defendi@helsinki.fi}
\date{\today}
\begin{document}
\maketitle

\section{Solutions} % (fold)
\label{sec:solutions}
\begin{exercise}
"Jason R. C. Nurse, T., 2020. Strava Storm: Why Everyone Should Check
Their Smart Gear Security Settings Before Going For A Jog. [online] Scientific
American. Accessed 9 December 2021.":
\begin{enumerate}
    \item An inversion attack was performed. The company 
		released a public heath-map to show people common paths that the
		users were doing around the world, and researchers analyzed the data
		trying to match possible locations of military basis.
	\item Sensor data layer, by the fact that the data from many users was
		exposed, and created an easy base for the attackers.
	\item Enabling the user to opt-out from the data collection, and reduce the
		range of visibility of other routes to a nearby radius. For military, it
		should be enforced that no third-party apps are used as fitness
		monitors. 
\end{enumerate}

Goodin, D., 2020. When Coffee Makers Are Demanding A Ransom, You Know Iot Is Screwed. [online]
Ars Technica. Accessed 9 December 2021. Link here
\begin{enumerate}
    \item The original firmware was replaced with a custom one, injected as it
		was a OTA update.
	\item The target was the firmware level, with goal to change the behavior of the
		machine, and turn the coffee machine to a cryptocurrencies miner. 
	\item Using code signing (when updating a firmware), encryption (HTTPS) and
		authentication (when accessing the machine's Wi-Fi). These may require a
		more powerful CU than the ESP8266.
\end{enumerate}

\end{exercise}
\begin{exercise}
\begin{enumerate}
    \item We concatenate identity and occupation and perform the sha256 hashing over the
string. The result of "Bruce Wayne" + " " + "Businessman" is
dd36c7c2458f2b6dfd06950561df777f39f8c5b7a6f5c5814cabbba5d5e2960a.
	\item We perform k-anonymity over the weights and the height of each
		identity. First sort the array (see notebook), take the interval of
		three numbers (3-anonymity) so that here only three persons can be
		identified. 
		\begin{table}[htpb]
		    \centering
		    \caption{3-anonymity}
		    \label{tab:label}
		    \begin{tabular}{|c | c|}
				\hline
				Weight & Height\\
				\hline
				56-66 & 170-178\\
				75-80 & 178-180\\
				88-96 & 182\\
				100-107 & 185-187\\
				107-147 & 187-191\\
				\hline
		    \end{tabular}
		\end{table}
		\begin{table}[htpb]
		    \centering
		    \caption{2-anonymity}
		    \label{tab:label}
		    \begin{tabular}{|c | c|}
			\hline
		     Weight & Height\\
			 \hline
			 56-57 & 170-177\\
			 66-75 & 177-180\\
			 76-80 & 182\\
			 88-91 & 185\\
			 95-100 & 187-191\\
			 102-107 &  \\
			 135-147& \\
			 \hline

		    \end{tabular}
		\end{table}\\
		In 3-anonymity, picking the height 182, we can identify Flash, Green Lantern, and Wonder
		Woman.\\
		In 2-anonymity, picking a weight between 95 and 100 can be Batman or
		Captain America. 

\end{enumerate}
    
\end{exercise}

\begin{exercise}
We found the respective averages $avg_{total} = 91,14285714$ and $avg_{no-Bruce}=90,84615385$.
We invert the formula, and do 
\[
	b_{total} = \sqrt{\frac{1}{2 avg_{total}}(-|x|)} = 2.6457513111060598 
\]. 
Removing B. Wayne from the list and comparing with the respective average, we
get:
\[
	b_{no-Bruce} = \sqrt{\frac{1}{2 avg_{no-Bruce}}(-|x|)} = 2.6500682974358214 
\].  
Therefore $\epsilon_{total} = 0,378, \epsilon_{no-Bruce} = 0,377$, which doesn't
tell if Bruce was considered in the calculation or not.  

\end{exercise}

% section solutions (end)

\medskip

\printbibliography

\doclicenseThis

\end{document}
